QPLIB: A Library of Quadratic Programming Instances

### 2016-07-19 QPLIB-2.2.tex
comments and minor corrections from first proofreading

Our taxonomy is based on a three-fields code of the form ``\textit{FVC}'', where \textit{F} indicates the objective function, \textit{V} the variables, and \textit{C} the constraints of the problem. The fields can be given the following values:
%
\begin{itemize}
 \item objective function: (L)inear, (D)iagonal convex quadratic, (C)onvex quadra-tic, nonconvex (Q)uadratic;
 %
 \item variables: (C)ontinuous only, (B)inary only, (M)ixed binary and continuous, (I)nteger only, (G)eneral (all threee types);
 %
 \item constraints: (N)one, (B)ox, (L)inear, (C)onvex quadratic, nonconvex (Q)ua-dratic.
\end{itemize}
%
The wildcard ``*'' will be used to indicate any possible choice, and lists of the form ``\{X, Y, Z\}'' will indicate that the value of the given field can freely attain any of the specified values.

@@

% -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -
\subsubsection{Examples and reformulations}\label{ssec:reform}

@@

When a $Q^i$ is positive semidefinite (SDP), i.e., the corresponding constraint/objective function is convex, general quadratic constraints are in fact equivalent to diagonal ones. In fact, every SDP matrix can be factorized as $Q^i = L^i (L^i)^\top$, e.g.~by the (incomplete) Cholesky factorization, $f^i(x) = x^\top Q^i x = \sum_{j \in \Mcn} z^2_jz$ where $z = x^\top L^i$. Hence, one could think that D** problems need not be distinguished from C** ones; however, this is true only for ``complicated'' constraints, but not for ``simple'' ones, because the above reformulation technique introduces linear constraints. Indeed, while C*L (and, a fortiori, C*\{C,Q\}) can always be brought to D*L (D*\{C,Q\}), using the same technique C*B becomes D*L, which is significantly different from D*B. In practice, a diagonal convex objective function under linear constraints is found in many applications ({\bf citations?}), so that D*L still makes sense to distinguish the case where the objective function is ``naturally'' separable from that where separability is artificially introduced, although this is in theory always possible. Conversely, there is usually little gain in distinguishing between **C problems and ``**D'' ones where the constraints are restricted to be diagonal, as there are much fewer cases where this naturally occurs ({\bf to the best of my knowledge}). This is why we did not include a ``D'' option for the constraints.

@@

  \item \emph{Nononvex Integer Quadratic Programs} QGQ is the more general, and therefore is the most general, class. Due to the lack of convexity even when integrality requirements are removed, solution methods must typically combine several algorithmic ideas, such as enumeration (distinguishing the role of integral variables from that of continuous ones involved into nonconvex terms) and techniques (e.g., outer approximation, SDP relaxation, \ldots) that allow to efficiently compute bounds. As in the convex case, QBQ, QMQ, and QIQ can benefit from more specific properties of the variables ({\bf citations?}).

>>>>

Our taxonomy is based on a three-fields code of the form ``\textit{FVC}'', where \textit{F} indicates the objective function, \textit{V} the variables, and \textit{C} the constraints of the problem. The fields can be given the following values:\todo{\small Ambros: maybe OVC instead of FVC?}
%
\begin{itemize}
 \item objective function: (L)inear, (D)iagonal convex quadratic, (C)onvex quadra-tic, nonconvex (Q)uadratic;
 %
 \item variables: (C)ontinuous only, (B)inary only, (M)ixed binary and continuous, (I)nteger only, (G)eneral (all threee types);
 %
 \item constraints: (N)one, (B)ox, (L)inear, (C)onvex quadratic, nonconvex (Q)ua-dratic.
\end{itemize}
%
The wildcard ``*'' will be used to indicate any possible choice, and lists of the form ``\{X, Y, Z\}'' will indicate that the value of the given field can freely attain any of the specified values.

@@

% -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -
\subsubsection{Examples and reformulations}\label{ssec:reform}
\todo{\small Ambros: maybe switch this with the next section? the next one contains more familiar material to the reader and might be an easier first introduction to the notation.}

@@

When a $Q^i$ is positive semidefinite (SDP), i.e., the corresponding constraint/objective function is convex, general quadratic constraints are in fact equivalent to diagonal ones. In fact, every SDP matrix can be factorized as $Q^i = L^i (L^i)^\top$,\todo{\small Ambros: did you really mean the same $L^i$ as above?} e.g.~by the (incomplete) Cholesky factorization, $f^i(x) = x^\top Q^i x = \sum_{j \in \Mcn} z^2_jz$ where $z = x^\top L^i$. Hence, one could think that D** problems need not be distinguished from C** ones; however, this is true only for ``complicated'' constraints, but not for ``simple'' ones, because the above reformulation technique introduces linear constraints. Indeed, while C*L (and, a fortiori, C*\{C,Q\}) can always be brought to D*L (D*\{C,Q\}), using the same technique C*B becomes D*L, which is significantly different from D*B. In practice, a diagonal convex objective function under linear constraints is found in many applications ({\bf citations?}), so that D*L still makes sense to distinguish the case where the objective function is ``naturally'' separable from that where separability is artificially introduced, although this is in theory always possible. Conversely, there is usually little gain in distinguishing between **C problems and ``**D'' ones where the constraints are restricted to be diagonal, as there are much fewer cases where this naturally occurs ({\bf to the best of my knowledge}). This is why we did not include a ``D'' option for the constraints.

@@

  \item \emph{Nonconvex Integer Quadratic Programs} QGQ is the more general, and therefore is the most general, class. Due to the lack of convexity even when integrality requirements are removed, solution methods must typically combine several algorithmic ideas, such as enumeration (distinguishing the role of integral variables from that of continuous ones involved into nonconvex terms) and techniques (e.g., outer approximation, SDP relaxation, \ldots) that allow to efficiently compute bounds. As in the convex case, QBQ, QMQ, and QIQ can benefit from more specific properties of the variables ({\bf citations?}).

### 2016-07-19 QPLIB.tex
comments and minor corrections from first proofreading

\usepackage{url}
\usepackage{secdot}
\usepackage{color}
\usepackage{booktabs}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{multirow}

@@

\begin{abstract}
 This paper describes a new instance library for Quadratic Programming (QP). QP is a very ``varied'' class, comprising sub-classes of problems ranging from trivial to undecidable. Solution methods for QP are very diverse, ranging from entirely combinatorial ones to completely continuous ones, to many where both aspects are fundamental. Selecting a set of instances of QP that is at the same time not overwhelmingly difficult and sufficiently challenging for the many different interested communities is therefore important. 
 %In order to help our selection process 
 We propose a simple taxonomy for QP instances that leads to a systematic problem selection mechanism. We then briefly survey the field of QP, giving an overview of theory, methods and solvers. Finally we describe how the library was put together, and detail its final contents.
\end{abstract}

>>>>

\usepackage{url}
\usepackage{secdot}
\usepackage{color}
\usepackage{booktabs}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{todonotes}

@@

\begin{abstract}
 This paper describes a new instance library for Quadratic Programming (QP). QP is a very ``varied'' class, comprising sub-classes of problems ranging from trivial to undecidable. Solution methods for QP are very diverse, ranging from entirely combinatorial ones to completely continuous ones, including many for which both aspects are fundamental. Selecting a set of instances of QP that is at the same time not overwhelmingly difficult and sufficiently challenging for the many different interested communities is therefore important. 
 %In order to help our selection process 
 We propose a simple taxonomy for QP instances that leads to a systematic problem selection mechanism. We then briefly survey the field of QP, giving an overview of theory, methods and solvers. Finally we describe how the library was put together, and detail its final contents.
\end{abstract}
